Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654

### 2016-07-08 WRITEUP/ms.tex
done abstract

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
The spinning black hole in RXJ1131 is quadruply-imaged by a foreground galaxy at $z$\ssim0.3.
This is the first resolved \bco imaging at intermediate redshift.
We perform a dynamical lens modeling on the spatially and spectrally resolved \bco line emission.
Dynamical lens modeling, the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
turbulent disk
is indicative of, and suggests...
The lensing-corrected molecular gas of $M_{\rm gas}$\eq1.38\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
We thus conclude that RXJ1131 a wet minor merger.
Fitting dust SED models, we derive a lensing-corrected dust mass of $M_{\rm dust}$ = 4\E{8}\,\Msun and a lensing-corrected \LIR\ssim1.5\E{12}\,\Lsun, corresponding to a SFR$_{\rm FIR}$\eq120\pmm63 \sfrU . 
This implies that the merger system of RXJ1131 is dusty in nature with ongoing starbursts. 
Dusty
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
%Demonstrate the first dynamical constraint on the MBH-sigma relation at intermediate redshift.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between baryonic physics/process
(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how baryons of present-day galaxies were assembled, 
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by 
a rapidly decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}. 
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and 
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift 
$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed --- 
only unresolved CO observations have been carried out for $\sim$$70$ ULIRGs up to date \citep{Combes11a, Combes13a}.

>>>>

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the ``Einstein ring''
RXS J1131$-$1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
Our observations detect a CO-emitting source near RXJ1131, confirming the presence of an optically 
faint companion reported in previous studies. 
Based on our dynamical lens modeling of the spatially and spectrally resolved \bco emission, 
we reconstruct a symmetric velocity gradient in the source plane and 
find an intrinsically symmetric double-horned line profile, which are suggestive of a 
rotating disk morphology, consistent with previous optical studies.
We find a lensing-corrected gas mass of $M_{\rm gas}$\ssim1.4\E{10}\,\Msun in the host galaxy and 
\ssim2\E{9}\,\Msun in the companion (gas mass ratio $\sim$7:1). 
The CO disk is extended over $\sim$6\,kpc, which yields a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun
for the host galaxy. This corresponds to a gas mass fraction of $\sim$19\%, confirming its gas-rich nature.
This fraction also confirms the trend of decreasing gas fraction since $z$\ssim1, which is responsible for the decline of
the cosmic \SF rate and black hole accretion rate densities.
Fitting dust SED models, we derive a lensing-corrected dust mass of $M_{\rm dust}$ = 4\E{8}\,\Msun, a 
lensing-corrected $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and a SFR$_{\rm FIR}$\eq120\pmm63 \sfrU, 
confirming the dusty nature of the merger.
A comparison of the gas and stellar distributions reveals active starbursts embedded 
within the molecular gas reservoir which is likely a result from merger-driven gas inflow.
The nature of RXJ1131 is consistent with the picture predicted by model simulations, in which it will 
likely retain its disk component and evolve into small bulge disk galaxy upon merging.
Our study presents the first resolved CO imaging at intermediate redshift, 
which allows us to provide the first dynamical constraint on the \bhrelation relation at intermediate redshift.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between baryonic physics/processes
(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how baryons of present-day galaxies were assembled, 
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by 
a rapidly decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}. 
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and 
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift 
$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed --- 
only unresolved CO observations have been carried out for $\sim$$70$ ULIRGs up to date \citep{Combes11a, Combes13a}.
